Instructions for \confname{} Proceedings

### 2019-05-07 papers/EMNLP2019/data-collection.tex

Table~\ref{tab:XXX} gives an overview of the collection nodes, XXX, XXX, grouped into $7$~domains. (\textbf{Report only dataset after round0, with a note in caption/footnote referring to the checkpoint pruning.})
% \begin{itemize}
% \item rows: domains (if we go for long paper: then one row per collection node?)
% \item columns:
%   \begin{enumerate}
%   \item \# collection nodes
%   \item collection nodes (list)
%   \item \# unique VG names
%   \item example VG names
%   \item \# unique objects
%   \item \# unique images (? not sure if necessary; maybe only one of unique {objects, images})
%   \end{enumerate}
% \end{itemize}

@@

\subsection{Procedure} describe the crowdsourcing set-up and the task
TODO: Footnote: we ran pilot experiments to design our experiment and instructions.
\paragraph{Collection Method}
\begin{itemize}
	\item instructions; put layout in appendix
	\item each round: HIT of 10 instances, collect 9~annotations for each HIT
	\item round 0 (with opt-outs) $\rightarrow$ pruning $\rightarrow$ rounds 1-3 (no opt-outs)\\
	pruning: Based on given opt-outs: keep images with no OCCLUSION, at most BBOX is ambiguous twice, at most 17\% of names in plural form, most frequent names is of same domain as VG name (gives $25,596$, i.e., discard $5,497$ instances)
	\item workers could only participate in one round, such as to avoid workers annotating an instance more than once. 
\end{itemize}

>>>>

Table~\ref{tab:XXX} gives an overview of the collection nodes, XXX, XXX, grouped into $7$~domains. (\textbf{Report only dataset after round0, with a note in caption/footnote referring to the checkpoint pruning.})

\begin{table*}
\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
	\toprule
	          vehicles &            food & animals\_plants &           home &        buildings &             people &      clothing \\
	\midrule
	  train (954) &  pizza (518) &  giraffe (915) &  bed (888) &  house (340) &  boy (853) &  shirt (904) \\
	  car (642) &  cake (261) &  horse (822) &  bench (714) &  bridge (274) &  man (806) &  jacket (451) \\
	  plane (485) &  bread (186) &  cat (754) &  table (687) &  dugout (91) &  woman (766) &  coat (267) \\
	  airplane (479) &  sandwich (153) &  dog (654) &  desk (672) &  tent (53) &  girl (650) &  dress (190) \\
	  motorcycle (466) &  bun (143) &  zebra (461) &  counter (516) &  restaurant (33) &  lady (342) &  hat (77) \\
	  truck (465) &  cheese (110) &  cow (324) &  couch (366) &  overpass (23) &  guy (330) &  t-shirt (62) \\
	 boat (450) &  donut (78) &  bird (295) &  chair (365) &  grill (22) &  child (230) &  tie (51) \\
	  jet (106) &  salad (70) &  sheep (216) &  carpet (307) &  garage (18) &  batter (110) &  blazer (43) \\
	  aircraft (85) &  sauce (68) &  bull (48) &  bowl (219) &  hotel (16) &  kid (85) &  hood (26) \\
	  van (76) &  apple (33) &  flower (40) &  curtain (182) &  castle (14) &  skateboarder (80) &  cap (20) \\
	\bottomrule
\end{tabular}
	\caption{Overview of our dataset: Top-10 VG names for each domain (number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset1}}
\end{table*}

\begin{table*}
	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
	\toprule
	        animals\_plants &               vehicles &                        home &                clothing &                   buildings &                    food &                 people \\
	\midrule
	  ungulate.n.01 (2037) &  aircraft.n.01 (1208) &  furnishing.n.02 (5355) &  shirt.n.01 (968) &  house.n.01 (364) &  dish.n.02 (812) &  woman.n.01 (1768) \\
	 horse.n.01 (833) &  train.n.01 (957) &  vessel.n.03 (525) &  overgarment.n.01 (786) &  bridge.n.01 (297) &  baked\_goods.n.01 (770) &  man.n.01 (1167) \\
	  feline.n.01 (763) &  car.n.01 (727) &  kitchen\_utensil.n.01 (132) &  dress.n.01 (199) &  shelter.n.01 (169) &  foodstuff.n.02 (280) &  male\_child.n.01 (853) \\
	 dog.n.01 (688) &  motorcycle.n.01 (564) &  crockery.n.01 (92) &  headdress.n.01 (135) &  restaurant.n.01 (58) &  vegetable.n.01 (48) &  athlete.n.01 (396) \\
	  bird.n.01 (389) &  truck.n.01 (559) &  cutlery.n.02 (82) &  neckwear.n.01 (65) &  outbuilding.n.01 (31) &  edible\_fruit.n.01 (42) &  child.n.01 (333) \\
	  flower.n.01 (44) &  boat.n.01 (499) &  tool.n.01 (72) &  robe.n.01 (27) &  hotel.n.01 (19) &  beverage.n.01 (23) &  creator.n.02 (11) \\
	  rodent.n.01 (27) &  ship.n.01 (38) &  lamp.n.01 (34) &  glove.n.02 (7) &  housing.n.01 (17) &   &  professional.n.01 (5) \\
	 insect.n.01 (12) &   &   &  footwear.n.01 (5) &  place\_of\_worship.n.01 (12) &   &   \\
	  fish.n.01 (11) &   &   &   &   &   &   \\
	\bottomrule
\end{tabular}
	\caption{Overview of our dataset: Collection nodes for each domain (number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset2}}
\end{table*}

% \begin{itemize}
% \item rows: domains (if we go for long paper: then one row per collection node?)
% \item columns:
%   \begin{enumerate}
%   \item \# collection nodes
%   \item collection nodes (list)
%   \item \# unique VG names
%   \item example VG names
%   \item \# unique objects
%   \item \# unique images (? not sure if necessary; maybe only one of unique {objects, images})
%   \end{enumerate}
% \end{itemize}

@@

\subsection{Procedure} describe the crowdsourcing set-up and the task
TODO: Footnote: we ran pilot experiments to design our experiment and instructions.
\paragraph{Collection Method}
\begin{itemize}
	\item instructions; \\
	Appendix~\ref{app:instructions} gives the instructions as they were presented to the annotators. 
	\item each round: HIT of 10 instances, collect 9~annotations for each HIT
	\item round 0 (with opt-outs) $\rightarrow$ pruning $\rightarrow$ rounds 1-3 (no opt-outs)\\
	pruning: Based on given opt-outs: keep images with no OCCLUSION, at most BBOX is ambiguous twice, at most 17\% of names in plural form, most frequent names is of same domain as VG name (gives $25,596$, i.e., discard $5,497$ instances)
	\item workers could only participate in one round, such as to avoid workers annotating an instance more than once. 
\end{itemize}
